Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-06 Paper/paper.tex
Format update!
A lot has changed... but I think it's gonna do something funny again.

\titleformat{\chapter}[display]% NEW
    {\normalfont\begin{center}}{\chaptertitlename\ \thechapter}{12pt}{}% NEW
\titlespacing*{\chapter}{0pt}{30pt}{20pt}% NEW

%\titleformat{\chapter}[block]{first}{label}{12pt}

\titleformat{\chapter}{}{\thesection}{1em}{}
\titleformat{\section}{}{\thesubsection}{1em}{}
\titleformat{\subsection}{}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{}{\theparagraph}{1em}{}

@@

\setcounter{tocdepth}{2}

@@

% - Asynchronous shennanigans
The addition of JavaScript to web applications led to a golden age of feature-rich applications with exciting user interface (UI) features that had not before been seen. This set of features and UI improvements came with the complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads but is stuck with just the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, loading data separately so as not to hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

@@

\subsection{Versioning}
Web applications can be updated at any time with instant roll-out and feedback. It requires absolutely no user interaction because the web page always serves the latest resources. In comparison to something like Microsoft Office that requires users to manually update, this feature leads to applications that can address problems quickly, roll-out security updates instantly, and incorporate consumer feedback much more quickly than any other type of software. For example, Google Docs is becoming incredibly popular as an online document editing suite. Updates to Google Docs are rolled out frequently and require little to no input from the user. Another perk is that users are not given a choice. This can lead to occasional customer outrage, but more often than not it's a powerful gain for both feature improvement and application security. There is no need to support legacy systems that may contain serious bugs.

@@

The developer is not free from all worry as they must still consider differing web browsers. This problem, however, is almost fully remedied by a number of online APIs that will rework underlying code based on browser versions and types.

@@

\subsubsection{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation application. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% Sample App 
%%%   Talk about test app
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Testing Frameworks Survey}
In the following chapter we will discuss the testing frameworks that we looked at and the application we used to evaluate them.

@@

\subsection{The Average Web Application}
In an effort to create a good workflow and collection of tools, we have chosen to focus on web applications that uses Node.js, JavaScript, Cloud Services, and a backing Database when searching for our tools. This choice was made because of the popularity of that kind of set up, as well as the fact that our evaluation application was set up in that way.

\todo{THIS IS LAME}
Although there are multiple languages and tools available for creating a backing server, we chose Node.js because of it's wide use and because it is what we're most familiar with.

JavaScript was chosen because it used in over 87\% of all websites. \cite{JSUsage} We also chose JavaScript because the rest of our application was written in JavaScript and we wanted to keep things as constant as possible.

Many web applications use Cloud Services for a number of things, most often they're used for storage of the web content that's being hosted.

Web applications tend to keep track of users which most often constitutes the use of a database behind the scenes to store users and update them as necessary.

@@

An important distinction that needs to be made is that in web applications there is functionality behind the scenes and there is the UI element of the web page. Unit testing frameworks are aimed at the functionality behind the scenes.

\subsection{Jasmine \cite{Jasmine}}
The first of the unit testing frameworks that we looked at was Jasmine, a Behavior Driven Development (BDD) testing framework. BDD is based on Test Driven Development and adds some simplifications and patterns that attempt to bring both developers and businessmen into the software testing process. The idea behind Behavior Driven Development is that input from non-technical stakeholders as well as technical stakeholders can come together so that everyone understands what the project should do.

@@

  it("should be able to subtract numbers", function () {
    var theAnswer = 10;
    expect(12 - 2).toEqual(theAnswer);
  });
});
\end{lstlisting}
The \lstinline{describe} statement creates a test suite to collect related tests under. Each \lstinline{it} statement is generally one test with some number of \lstinline{expect} statements. It may not be particularly pretty, but the above code is quite readable even to someone with no coding experience.

The default Jasmine package had some ineptitudes in dealing with Node.js but there was a package available through npm called jasmine-node \cite{JasmineNode} that gave jasmine access to the node package and functions.

Asynchronous testing using Jasmine was a bit of a chore, but there is support built in. This support comes in the form of a three-set function progression. The first function, \lstinline!runs(function () { .... })!, runs the asynchronous code. The second function, \lstinline!waitsFor(function () { ... })!, waits for a true value from a flag or other system. Finally, the third function, another \lstinline{runs(...)}, houses the assertions to determine if the code ran properly or not. This method requires a fairly substantial amount of typing as well as complicated function chains when more than one asynchronous call is required.

@@

Jasmine is an interesting take on testing that we'd not see before, the BDD system in particular. We like the way assertions and tests are written in such a stylized manner. The asynchronous support is there but a bit tedious.

\subsection{Mocha \cite{Mocha}}
Mocha is another BDD testing framework that is almost identical to Jasmine. Unlike Jasmine, however, Mocha is not completely self-contained and requires an additional assertion library of one's choosing. We will outline our choice of Chai.js below.

Mocha, by default, also uses the \lstinline{describe -> it("should..."} pattern to create tests. Mocha offers a variety of other test interfaces for developer's to write their test code as well as a custom, nearly unstructured variety. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

// QUnit
suite('QUnit Suite');
test('test 1', function () {
  ...
});
\end{lstlisting}
The developer doesn't gain anything by using one interface over another except the ability to write tests in a way that makes sense to them. There is no standard for writing assertions, as each assertion library is likely to be slightly different.

@@

Overall Mocha offered more flexibility and better asynchronous support at the cost of additional setup. This increased flexibility came in the way of being able to select our own testing interface and assertion library so that our tests looked the way we wanted them. The cost of that was the need to find our own assertion library among the dozen that are out there. We prefer Mocha's method of asynchronous testing because it required considerably less typing on our part and was more easy to follow and read than the Jasmine chain of method calls.

\subsubsection{Chai.js \cite{Chaijs}}
For the assertion library we chose Chai.js.  It offers the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to a nice developer experience that can appeal to a variety of different developers.

\subsection{QUnit \cite{QUnit}}
QUnit is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, an immensely popular framework for DOM manipulation and access. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the \lstinline{it} functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png}
  \captionof{figure}{Each individual spec is further broken down into the assertions within it.}
\end{Figure}

An interesting feature that QUnit has that we'd not seen elsewhere is the ability to specify how many assertions are expected to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

QUnit isn't perfect however, QUnit tests are not grouped into suites by default and the syntax for grouping them leaves much to be desired. In order to group tests into ``modules'', as QUnit calls them, the developer writes code like the following:
\begin{lstlisting}
Qunit.module("Module A"); // All code following is grouped
test("Addition", function () {
  equal(2 + 2, 4, "Two + Two = Four");
  equal(3 + 5, 8, "Three + Five = Eight");
});
test("Subtraction", function () {
  equal(4 - 2, 2, "Four - Two = Two");
  equal(2 - 2, 0, "Two - Two = Zero");
});

@@

QUnit.module("Module B");
// Tests now grouped under Module B
// ... Etc
\end{lstlisting}
It is difficult to visually see where one module starts and ends and so grouping and finding the right place to add a test can be a chore.

@@

QUnit was a particularly strong contender when we saw the table that was produced after running the tests but its shortcomings led us to keep looking elsewhere. QUnit's handling of asynchronous tests is nice because they are more explicitly stated for the casual read-through instead of an extra parameter or set of functions within the test itself.

\subsection{Intern\cite{InternIO}}
Intern is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of the inability to set up cross-server communication easily and properly.

%-AMD
Intern uses Asynchronous Module Definition (AMD) form which is something we'd not seen before. Where this comes into play is merely in what used to be \lstinline{require(...)}. Instead of separately requiring modules, the entire program is wrapped in a \lstinline{define([...])} block that passes modules as parameters to an overarching function. That will make more sense after an example:
\begin{lstlisting}
// Intern
define([
    'intern!object',
    'intern/chai!assert',
    'app/hello'
], function (registerSuite, assert, hello) {
  // Test code here
});

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas. \cite{AMDInfo} Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because of the maturity of the evaluation project.

@@

Intern offered a one-stop shop for all of our testing needs but fell short when it came to configuring it for our Node.js server setup. If we had a more traditional web application setup with a separate server that served normal HTML pages, Intern would have likely been our go-to tool for all of our testing needs.

@@

\subsection{Selenium\cite{Selenium}}
Selenium is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

Selenium's Node incarnation is out-of-date and as such we had to change the Selenium package to use the latest version of Selenium that works with the latest version of browsers. This required us to edit some of the JavaScript files that ran Selenium from the console using Node. At the time of this writing, the Selenium node package was using Selenium 2.20 from over two years ago. The latest Selenium version is 2.40.

@@

\subsection{Nightwatchjs\cite{NightwatchJS}}
Nightwatch is a JavaScript testing library that wraps Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

In addition to being more verbose, I've had to add an assertion library and this code has to be run using Node.js and the Mocha module instead of using the Selenium command.

@@

\subsubsection{PhantomJS\cite{PhantomJS}}
The reigning king of headless browsers is PhantomJS. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

\subsubsection{ZombieJS\cite{ZombieJS}}
ZombieJS is often the other go-to for headless browsers. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

\subsection{Jenkins \cite{Jenkins}}
Jenkins is the first of the continuous integration frameworks that we tried out. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

@@

\subsection{Travis \cite{Travis}}
Travis is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

\subsection{Semaphore \cite{Semaphore}}
Semaphore is another online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

@@

\subsection{MagnumCI \cite{MagnumCI}}
MagnumCI is another online CI framework, it appears that Jenkins is one of the only ``off-line'' CI systems. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects, and that's what we care about.

@@

\subsection{Drone.io \cite{DroneIO}}
Drone.io is an impressive online CI framework that offers substantial language support, is free for open-source projects, and offers the most reasonable pricing scheme for private repositories.

@@

\subsection{Sauce Labs\cite{SauceLabs}}
Sauce Labs is an online service that gives you access to a variety of browsers and browser options. They outline the options available to the developer as follows: Selenium, JavaScript, Mobile, Manual. Sauce Labs will start up a Selenium server and run the developer's Selenium tests, they can run unit tests using their JavaScript service, they allow access to a variety of mobile device browsers and resolution, and they offer the ability to manually look at a web application in different browser configurations.

@@

\subsection{Istanbul\cite{Istanbul}}
As already mentioned briefly, IStanbul is a tool used for code coverage metrics. It was built into Intern.io but getting it running with other frameworks is easy as well.

@@

\subsection{Grunt.js\cite{GruntJS}}
Grunt.js is a task-runner for JavaScript. What Grunt does is automate routine tasks like linting, testing, copying files, and updating modules. The developer writes Grunt scripts that outline the necessary tasks and then can run them on the commandline with the \lstinline{grunt} command.

@@

\subsection{Node Inspector\cite{NodeInspector}}
Node Inspector is a GitHub project for debugging Node.js server-side code. The inspector runs in the browser and is started by running \lstinline{node-debug} instead of \lstinline{node} when starting the application. Simple as that. Then you can set breakpoints using the normal browser developer tools.

@@

\section{PolyXpress (PX)\cite{PX}}
Our major evaluation application was an in-house application called PolyXpress (PX). As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Since the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the appendix at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the appendix now.

@@

\subsection{``A Framework for Automated Testing of JavaScript Web Applications'' \cite{FrameworkForAutomatedTesting}}
A collection of IBM Researchers and two university students came up with a framework called ``Artemis'' for testing web applications. What is novel about their tool is that it generates test cases automatically based on execution patterns and feedback. They have attempted to solve the problem that writing test cases by hand is both time-consuming and often difficult. Their automatic test generation lead to an average of 69\% test coverage with enough tests generated.

@@

\subsection{``A Multi-Agent Software Environment for Testing Web-based Applications'' \cite{MultiAgentSoftwareEnvironment}}
Two students and a person from Lanware Limited brought AI into the web testing world with an agent-based environment for testing web applications. In order to split testing into manageable tasks for agents to carry out, they created an ontology for web testing using XML. Each agent is set up to handle one particular kind of testing with certain test data, i.e., a unit tester with data for one or two functions. This agent may then communicate with another agent who needs the results from that test, such as a test coverage agent or agent that is keeping track of test success and failure. This communication is done through a message-passing intermediary layer and a set of brokers who shuffle messages between agents.

@@

\subsection{Author Model Unit Test}
...

\subsection{Author Controller Unit Test}
...

\subsection{Author Server Unit Test}
...

>>>>

\titleformat{\chapter}[display]% NEW
    {\normalfont\centering}{\chaptertitlename\ \thechapter}{12pt}{}% NEW
\titlespacing*{\chapter}{0pt}{30pt}{20pt}% NEW

%\titleformat{\section}[block]{first}{label}{12pt}

\titleformat{\section}{}{\thesection}{1em}{}
\titleformat{\subsection}{}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}{}{\theparagraph}{1em}{}

@@

\setcounter{tocdepth}{3}

@@

% - Asynchronous shennanigans
The addition of JavaScript to web applications led to a golden age of feature-rich applications with exciting user interface (UI) features that had not before been seen. This set of features and UI improvements came with the complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads, they only have access to the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, loading data separately so as not to hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

@@

\subsection{Versioning}
Web applications can be updated at any time with instant roll-out and feedback. It requires absolutely no user interaction because the web page always serves the latest resources. In comparison to something like Microsoft Office that requires users to manually update, this feature leads to applications that can address problems quickly, roll-out security updates instantly, and incorporate consumer feedback much more often than any other type of software. For example, Google Docs is becoming incredibly popular as an online document editing suite. Updates to Google Docs are rolled out frequently and require little to no input from the user. Another perk is that users are not given a choice. This can lead to occasional customer outrage, but more often than not it is a powerful gain for both feature improvement and application security. There is no need to support legacy systems that may contain serious bugs.

@@

The developer is not free from all worry as they must still consider differing web browsers. This problem, however, is almost fully remedied by a number of online APIs, such as jQuery\cite{jQuery}, that will rework underlying code based on browser versions and types.

@@

\subsection{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation application. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% Sample App 
%%%   Talk about test app
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Testing Frameworks Survey}
In the following chapter we will discuss the testing frameworks that we looked at and the application we used to evaluate them. This chapter will conclude with a set of decision matrices outlining the strengths of each individual framework and where they overlap.

@@

\subsection{The Average Web Application}
\todo{Re-write this section}

% In an effort to create a good workflow and collection of tools, we have chosen to focus on web applications that uses Node.js, JavaScript, Cloud Services, and a backing Database when searching for our tools. This choice was made because of the popularity of that kind of set up, as well as the fact that our evaluation application was set up in that way.

% \todo{THIS IS LAME}
% Although there are multiple languages and tools available for creating a backing server, we chose Node.js because of it's wide use and because it is what we're most familiar with.

% JavaScript was chosen because it used in over 87\% of all websites. \cite{JSUsage} We also chose JavaScript because the rest of our application was written in JavaScript and we wanted to keep things as constant as possible.

% Many web applications use Cloud Services for a number of things, most often they're used for storage of the web content that's being hosted.

% Web applications tend to keep track of users which most often constitutes the use of a database behind the scenes to store users and update them as necessary.

@@

Web applications can be broken down into two general parts. There is functionality behind the scenes that drives the web page and there is the user interface of the web page that conveys the information to the user. Unit testing frameworks are aimed at the functionality the drives the web page, not what the user sees.

\subsection{Jasmine}
The first of the unit testing frameworks that we looked at was Jasmine\cite{Jasmine}, a Behavior Driven Development (BDD) testing framework. BDD is based on Test Driven Development and adds some simplifications and patterns that attempt to bring both developers and businessmen into the software testing process. The idea behind Behavior Driven Development is that input from non-technical stakeholders as well as technical stakeholders can come together so that everyone understands what the project should do.

@@

  it("should be able to subtract numbers", function () {
    var theAnswer = 10;
    expect(12 - 2).toEqual(theAnswer);
  });
});
\end{lstlisting}
The \lstinline{describe} statement creates a test suite to collect related tests under. Each \lstinline{it} statement is generally one test with some number of \lstinline{expect} statements. The above code is quite readable even to someone with no coding experience.

The default Jasmine did not support Node.js but there was a package available through npm called jasmine-node \cite{JasmineNode} that gave jasmine access to the node package and functions.

Asynchronous testing using Jasmine is a bit of a chore because it requires a series of functions that are not straightforward, but there is support built in. This support comes in the form of a three-set function progression. The first function, \lstinline!runs(function () { .... })!, runs the asynchronous code. The second function, \lstinline!waitsFor(function () { ... })!, waits for a true value from a flag or other system. Finally, the third function, another \lstinline{runs(...)}, houses the assertions to determine if the code ran properly or not. These functions will be outlined in an example below. This method of asynchronous testing requires a fairly substantial amount of typing as well as complicated function chains when more than one asynchronous call is required.

@@

Jasmine's BDD testing is something that we'd not see before. Having come from a more structured and developer-oriented testing background, it was interesting to see assertions and tests written in this different manner. The idea behind writing tests in this style is that requirements and customer feedback can be more easily translated into tests or even written by customers or other non-technical stakeholders. Jasmine does have asynchronous support but the three-function system is a bit tedious.

\subsection{Mocha}
Mocha\cite{Mocha} is another BDD testing framework that is almost identical to Jasmine. Unlike Jasmine, however, Mocha is not completely self-contained and requires an additional assertion library of one's choosing. We will outline our choice of Chai.js below.

Mocha, by default, also uses the \lstinline{describe -> it("should..."} pattern to create tests. Mocha offers a variety of other test interfaces for developers to write their test code. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

// QUnit
suite('QUnit Suite');
test('test 1', function () {
  ...
});

// Require, allows the developer to structure and call tests what they want
var testCase = require('mocha').describe

testCase('Require Suite', function(){
  testCase('test 1', function(){
    ...
  });
});
\end{lstlisting}
The developer doesn't gain anything by using one interface over another except the ability to write tests in a way that makes sense to them. There is no standard for writing assertions, as each assertion library is likely to be slightly different.

@@

Overall Mocha offered more flexibility and better asynchronous support at the cost of additional setup. This increased flexibility came in the way of being able to select a testing interface and assertion library so that tests could be written in the way a developer wants. The cost of the flexibilty was the need to find an assertion library among the dozen that are out there. We prefer Mocha's method of asynchronous testing because it required considerably less typing on our part and was more easy to follow and read than the Jasmine chain of method calls.

\subsubsection{Chai.js}
For the assertion library we chose Chai.js\cite{Chaijs}. It contains three different assertion APIs: an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to a nice developer experience that can appeal to a variety of different developers.

\subsection{QUnit}
QUnit\cite{QUnit} is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, a popular framework for DOM manipulation and access\cite{jQuery}. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the \lstinline{it} functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png}
  \captionof{figure}{Each individual spec is further broken down into the assertions within it.}
\end{Figure}

An interesting feature that QUnit has that we'd not seen elsewhere is the ability to specify how many assertions are expected to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. Silent failure can happen if the developer forgets to specify that a test is asynchronous or if there are synchronous callbacks. If a function in the test has a callback that runs the assertions, the test framework may finish executing the test and move on to the next test before ever running the assertions in the callback. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

QUnit tests are not grouped into suites by default and the syntax for grouping them leaves much to be desired. In order to group tests into ``modules'', as QUnit calls them, the developer writes code like the following:
\begin{lstlisting}
Qunit.module("Module A"); // All code following is grouped
test("Addition", function () {
  equal(2 + 2, 4, "Two + Two = Four");
  equal(3 + 5, 8, "Three + Five = Eight");
});
test("Subtraction", function () {
  equal(4 - 2, 2, "Four - Two = Two");
  equal(2 - 2, 0, "Two - Two = Zero");
});

@@

QUnit.module("Module B");
// Tests now grouped under Module B
// ... Etc
\end{lstlisting}
It can be difficult to visually see where one module starts and ends, resulting in additional time spent finding the right place to add a test.

@@

QUnit provides another style of writing tests and grouping modules. QUnit's handling of asynchronous tests is nice because they are more explicitly stated for the casual read-through instead of an extra parameter or set of functions within the test itself.

\subsection{Intern}
Intern\cite{InternIO} is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. It is our intention to build a testing framework with all of these components, so finding a framework with all of them built-in was promising. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of our inability to set up cross-server communication due to inexperience.

%-AMD
Intern uses Asynchronous Module Definition (AMD) form. This is merely a change in how modules are included in a piece of code, instead of separately requiring modules, the entire program is wrapped in a \lstinline{define([...])} block that passes modules as parameters to an overarching function. That will make more sense after an example:
\begin{lstlisting}
// Intern
define([ // Here's the AMD
    'intern!object',
    'intern/chai!assert',
    'app/hello'
], function (registerSuite, assert, hello) {
  // Test code here
});

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas. \cite{AMDInfo} Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because that is what Node.JS uses, which is used by our evaluation applications.

@@

Intern offers a fully-featured framework for all testing needs but was difficult to configure for a Node.js server setup. If a developer had a more traditional web application setup with a separate server that served normal HTML pages, Intern would be a go-to framework for all testing needs.

@@

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

% This is talked about in the tutorial
% Selenium's Node incarnation is out-of-date and as such we had to change the Selenium package to use the latest version of Selenium that works with the latest version of browsers. This required us to edit some of the JavaScript files that ran Selenium from the console using Node. At the time of this writing, the Selenium node package was using Selenium 2.20 from over two years ago. The latest Selenium version is 2.40.

@@

\subsection{Nightwatchjs}
Nightwatch\cite{NightwatchJS} is a JavaScript testing library that wraps Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

In addition to being more verbose, we've had to add an assertion library and this code has to be run using Node.js and the Mocha module instead of using the Selenium command. By default, Selenium does not come with its own assertion library. We chose Mocha with Chai.js because we were most familiar with it.

@@

\subsubsection{PhantomJS}
The reigning king of headless browsers is PhantomJS\cite{PhantomJS}. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

\subsubsection{ZombieJS}
ZombieJS\cite{ZombieJS} is often the other go-to for headless browsers. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

\subsection{Jenkins}
Jenkins\cite{Jenkins} is the first of the continuous integration frameworks that we tried out. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

@@

\subsection{Travis}
Travis\cite{Travis} is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

\subsection{Semaphore}
Semaphore\cite{Semaphore} is another online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

@@

\subsection{MagnumCI}
MagnumCI\cite{MagnumCI} is another online CI framework, it appears that Jenkins is one of the only ``off-line'' CI systems. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects, and that's what we care about.

@@

\subsection{Drone.io}
Drone.io\cite{DroneIO} is an impressive online CI framework that offers substantial language support, is free for open-source projects, and offers the most reasonable pricing scheme for private repositories.

@@

\subsection{Sauce Labs}
Sauce Labs\cite{SauceLabs} is an online service that gives you access to a variety of browsers and browser options. They outline the options available to the developer as follows: Selenium, JavaScript, Mobile, Manual. Sauce Labs will start up a Selenium server and run the developer's Selenium tests, they can run unit tests using their JavaScript service, they allow access to a variety of mobile device browsers and resolution, and they offer the ability to manually look at a web application in different browser configurations.

@@

\subsection{Istanbul}
As already mentioned briefly, Istanbul\cite{Istanbul} is a tool used for code coverage metrics. It was built into Intern.io but getting it running with other frameworks is easy as well.

@@

\subsection{Grunt.js}
Grunt.js\cite{GruntJS} is a task-runner for JavaScript. What Grunt does is automate routine tasks like linting, testing, copying files, and updating modules. The developer writes Grunt scripts that outline the necessary tasks and then can run them on the commandline with the \lstinline{grunt} command.

@@

\subsection{Node Inspector}
Node Inspector\cite{NodeInspector} is a GitHub project for debugging Node.js server-side code. The inspector runs in the browser and is started by running \lstinline{node-debug} instead of \lstinline{node} when starting the application. Simple as that. Then you can set breakpoints using the normal browser developer tools.

@@

\section{PolyXpress (PX)}
Our major evaluation application was an in-house application called PolyXpress (PX)\cite{PX}. As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Since the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the appendix at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the appendix now.

@@

\subsection{``A Framework for Automated Testing of JavaScript Web Applications''}
A collection of IBM Researchers and two university students came up with a framework called ``Artemis'' for testing web applications\cite{FrameworkForAutomatedTesting}. What is novel about their tool is that it generates test cases automatically based on execution patterns and feedback. They have attempted to solve the problem that writing test cases by hand is both time-consuming and often difficult. Their automatic test generation lead to an average of 69\% test coverage with enough tests generated.

@@

\subsection{``A Multi-Agent Software Environment for Testing Web-based Applications''}
Two students and a person from Lanware Limited brought AI into the web testing world with an agent-based environment for testing web applications\cite{MultiAgentSoftwareEnvironment}. In order to split testing into manageable tasks for agents to carry out, they created an ontology for web testing using XML. Each agent is set up to handle one particular kind of testing with certain test data, i.e., a unit tester with data for one or two functions. This agent may then communicate with another agent who needs the results from that test, such as a test coverage agent or agent that is keeping track of test success and failure. This communication is done through a message-passing intermediary layer and a set of brokers who shuffle messages between agents.

@@

\subsection{Author Model Unit Test}
\begin{lstlisting}
var assert = require("chai").assert;
